Narrative

### 2023-05-20 manuscript/introduction.qmd
intro: improved final paragraph

It is difficult to predict the total effect of the negative and positive bias in heterogeneity due to unreliability. This depends on average effect size, the amount of heterogeneity, mean reliability across studies, the variability in reliabilities, and sampling variance within studies. Hence, we perform a Monte-Carlo simulation study to explore the expected bias in heterogeneity estimates when meta-analyzing primary studies with imperfect measurement reliabilities.

>>>>

It is difficult to predict the total effect of the negative and positive bias in heterogeneity due to unreliability, and existing literature tends to focus on the positive bias (e.g., Borenstein, 2009, p. 342; Card, 2015, p. 126; Hunter & Schmidt, 2015; Wiernick & Dahlke, 2020). However, given that the negative bias could often be 20% or more and the value of accurate  heterogeneity estimates for many research outcomes in psychology, we consider it important to have insight into the total bias in heterogeneity estimates that should be expected due to unreliability. This depends on average effect size, true heterogeneity, mean reliability across studies, the variability in reliabilities, and sampling variance within studies. Hence, we perform a Monte-Carlo simulation study to explore the expected bias in heterogeneity estimates when meta-analyzing primary studies with imperfect measurement reliabilities.
